---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# lmarr

<!-- badges: start -->
[![R-CMD-check](https://github.com/ranen0827/mypackage.11.15.2022/workflows/R-CMD-check/badge.svg)](https://github.com/ranen0827/mypackage.11.15.2022/actions)
<!-- badges: end -->


## Functions

* `lm_mat()` gives basic information of the variables from the linear model, as well as matrix notations useful for further calculation
* `coef1()` creates coefficient table of the linear model, calculate R squared and Adjusted R squared, as well as covariance matrix of the model
* `model_diag()` creates useful diagrams for model diagnostics (using residuals$\hat{\epsilon}$, fitted values $\hat{Y}$ and original values $\hat{Y}$)
* `eda()` creates useful diagrams for Exploratory Data Analysis (EDA) of the variables selected from data frames

## Installation

You can install the development version of package.test.11.15 from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("ranen0827/mypackage.11.15.2022")
```

## Usage

This is a basic example which shows you how to solve a common problem:

```{r example}
library(package.test.11.15)
## basic example code
head(mtcars)
#                   mpg cyl disp  hp drat    wt  qsec vs am gear carb
# Mazda RX4         21.0   6  160 110 3.90 2.620 16.46  0  1    4    4
# Mazda RX4 Wag     21.0   6  160 110 3.90 2.875 17.02  0  1    4    4
# Datsun 710        22.8   4  108  93 3.85 2.320 18.61  1  1    4    1
# Hornet 4 Drive    21.4   6  258 110 3.08 3.215 19.44  1  0    3    1
# Hornet Sportabout 18.7   8  360 175 3.15 3.440 17.02  0  0    3    2
# Valiant           18.1   6  225 105 2.76 3.460 20.22  1  0    3    1
model <- lm_mat("mpg", c("drat", "disp", "wt"), mtcars, beta0 = TRUE)
names(model)
# [1] "xvar"      "yvar"      "Dataset"   "selected"  "beta0"     "N"         "p"        
# [8] "X"         "Y"         "H"         "Y_hat"     "residuals"

coef1(model)
# $Coefficients
#                Estimate  Std.Error   t_value      p_value Sig.
# (Intercept) 34.66099474 2.54700388 13.608536 4.019007e-14  ***
# cyl         -1.58727681 0.71184427 -2.229809 3.366495e-02    *
# disp        -0.02058363 0.01025748 -2.006696 5.418572e-02    .

# $F_test
#                F_value df1 df2      p_value Sig.
# F test result 45.80755   2  29 1.057904e-09  ***

# $Signif.codes
# [1] "0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1"

# $Adj.R_square
# [1] 0.7429841

# $R_square
# [1] 0.7595658

# $Covariance_matrix
#             (Intercept)          cyl          disp
# (Intercept)  6.48722874 -1.615718386  0.0164777387
# cyl         -1.61571839  0.506722267 -0.0065863960
# disp         0.01647774 -0.006586396  0.0001052158
```


```{r model_diagnostics}
model_diag(model)
```



```{r eda}
eda(mtcars[,c(model$yvar, model$xvar)])
```


