---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# package.test.11.15

<!-- badges: start -->
[![R-CMD-check](https://github.com/ranen0827/mypackage.11.15.2022/workflows/R-CMD-check/badge.svg)](https://github.com/ranen0827/mypackage.11.15.2022/actions)
[![Codecov test coverage](https://codecov.io/gh/ranen0827/mypackage.11.15.2022/branch/master/graph/badge.svg)](https://app.codecov.io/gh/ranen0827/mypackage.11.15.2022?branch=master)
<!-- badges: end -->

## Simple/Multiple Linear Regression model  
If a single predictor X that has a linear relationship with a response y, we can build a regression model to analyze their relationship.

* Consider a SLR (Simple Linear Regression) model:
$$Y_{i} = \beta_{0}+\beta_{1}X_{i}+\epsilon_{i}$$
* Consider a MLR (Multiple Linear Regression) model:
$$Y_{i} = \beta_{0}+\beta_{1}X_{i}+\beta_{2}X_{i}+...+\beta_{p-1}X_{i}+\epsilon_{i}$$


## Regression Model without intercept  
* Sometimes we may not need intercept (e.g. Categorical variables with all dummy variables included in the model), we can conduct linear regression model without intercept, the model looks like this:  
$$Y_{i} = \beta_{1}X_{i}+\beta_{2}X_{i}+...+\beta_{p-1}X_{i}+\epsilon_{i}$$


## Functions

* `lm_mat()` gives basic information of the variables from the linear model, as well as matrix notations useful for further calculation
* `coef1()` creates coefficient table of the linear model, calculate R squared and Adjusted R squared, as well as covariance matrix of the model
* `model_diag()` creates useful diagrams for model diagnostics (using residuals $\hat{\epsilon}$, fitted values $\hat{Y}$ and original values $\hat{Y}$)
* `eda()` creates useful diagrams for *Exploratory Data Analysis* (EDA) of the variables selected from data frames

## Installation

You can install the development version of package.test.11.15 from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("ranen0827/mypackage.11.15.2022", build_vignettes = T)
```

## Usage

This is a basic example which shows you how to solve a common problem:

```{r example}
library(package.test.11.15)
## load dataset mtcars
head(mtcars)

## lm_mat() function -->
model <- lm_mat("mpg", c("drat", "disp", "wt"), mtcars, beta0 = TRUE)
names(model)

## coef1() function -->
coef1(model)
```


```{r model_diagnostics}
## model_diag() function -->
model_diag(model)
```



```{r eda}
## eda() function -->
eda(mtcars[,c(model$yvar, model$xvar)])
```


