---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# lmarr

<!-- badges: start -->
[![R-CMD-check](https://github.com/ranen0827/mypackage.11.15.2022/workflows/R-CMD-check/badge.svg)](https://github.com/ranen0827/mypackage.11.15.2022/actions)
[![Codecov test coverage](https://codecov.io/gh/ranen0827/mypackage.11.15.2022/branch/master/graph/badge.svg)](https://app.codecov.io/gh/ranen0827/mypackage.11.15.2022?branch=master)
<!-- badges: end -->


## Functions

* `lm_mat()` gives basic information of the variables from the linear model, as well as matrix notations useful for further calculation
* `coef1()` creates coefficient table of the linear model, calculate R squared and Adjusted R squared, as well as covariance matrix of the model
* `model_diag()` creates useful diagrams for model diagnostics (using residuals$\hat{\epsilon}$, fitted values $\hat{Y}$ and original values $\hat{Y}$)
* `eda()` creates useful diagrams for Exploratory Data Analysis (EDA) of the variables selected from data frames

## Installation

You can install the development version of package.test.11.15 from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("ranen0827/mypackage.11.15.2022")
```

## Usage

This is a basic example which shows you how to solve a common problem:

```{r example}
library(package.test.11.15)
## basic example code
head(mtcars)

model <- lm_mat("mpg", c("drat", "disp", "wt"), mtcars, beta0 = TRUE)
names(model)

coef1(model)
```


```{r model_diagnostics}
model_diag(model)
```



```{r eda}
eda(mtcars[,c(model$yvar, model$xvar)])
```


