---
title: "package_tutorial"
output: rmarkdown::html_vignette
description: 
vignette: >
  %\VignetteIndexEntry{lmarr_tutorial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(package.test.11.15)
```

## Basic ideas

-   Consider a MLR (Multiple Linear Regression) model: $$Y_{i} = \beta_{0}+\beta_{1}X_{1}+\beta_{2}X_{2}+\epsilon_{i}$$  
-   We will use the following four functions to conduct *exploratory data analysis*, *modeling* (including paramater estimation and inference), and *model diagnostics*.
-   The dataset in vignette is "mtcars" built in the R function. In test cases we use sample dataset "iris" from basic R function.

## `lm_mat`: Gets the matrix notation and basic information from outcome(Y) and predictors(X) constructing a linear model.

```{r}
## Input parameters, able to be edited
# Response variable
y <- c("mpg")
# Predictors
x <- c("cyl", "disp")
# Dataset
data <- mtcars
# Whether included beta0 or not
beta0 <- TRUE

model <- lm_mat(y, x, mtcars, beta0)
model1 <- lm(mpg~cyl+disp, data=mtcars)
## Variable names of the returned list
names(model)
```

The export list includes a set of variables as follows:

### Basic information:

-   `xvar`: A vector containing names of input predictors ($X$)\
-   `yvar`: A vector containing names of input response ($Y$)\
-   `Dataset`: Same as input dataset\
-   `selected`: Selected data frame of all required variables\
-   `beta0`: A boolean variable indicating whether the linear model includes intercept or not\
-   `N`: Number of row(s) (observation(s)) in the original dataset\
-   `p`: Number of parameters (beta's) in the linear model

### Matrix Notation:

-   `X`: Model design matrix\
-   `Y`: Response variable\
-   `H`: The "hat" matrix - $X(X^{T}X)^{-1}X^{T}$\
-   `Y_hat`: Fitted values, $\hat{Y}$\
-   `residuals`: Model residuals, $\hat{\epsilon}$

```{r}
## Using all.equal and bench::mark to check both correctness and efficiency of the function lm_mat
### Correctness using all.equal
stopifnot(all.equal(model$xvar,x)) # orders matter
stopifnot(all.equal(model$yvar,y))
stopifnot(all.equal(model$Dataset,data))
stopifnot(all.equal(model$selected,data[,c(y,x)]))
stopifnot(all.equal(model$beta0, beta0))
stopifnot(all.equal(model$N,nrow(data)))
stopifnot(all.equal(model$p,beta0 + length(x)))
stopifnot(all(model$X == matrix(c(rep(1,nrow(mtcars)), mtcars[,"cyl"], mtcars[, "disp"]), nrow(mtcars), 3)))
stopifnot(all.equal(c(model$Y),data[,y]))
X <- matrix(c(rep(1,nrow(data)), data[,x[1]], data[,x[2]]),nrow(data),3)
stopifnot(all.equal(model$H, X %*% solve(t(X) %*% X) %*% t(X)))
stopifnot(all.equal(model$Y_hat, X %*% solve(t(X) %*% X) %*% t(X) %*% data[,y]))
stopifnot(all.equal(model$residuals, data[,y] - c(X %*% solve(t(X) %*% X) %*% t(X) %*% data[,y])))
print("all the return values from function 'lm_mat' have been verified")

### Efficiency using bench::mark
bench::mark(model$xvar, c("cyl", "disp"))

bench::mark(
  model$yvar,
  c("mpg"))

bench::mark(
  model$p,
  beta0+length(c("cyl", "disp")))

bench::mark(
  model$X[,1],
  matrix(c(rep(1,nrow(data)), mtcars[,"cyl"], mtcars[, "disp"]), nrow(mtcars), 3)[,1])

bench::mark(
  model$X[,2],
  matrix(c(rep(1,nrow(data)), mtcars[,"cyl"], mtcars[, "disp"]), nrow(mtcars), 3)[,2])

bench::mark(
  model$X[,3],
  matrix(c(rep(1,nrow(data)), mtcars[,"cyl"], mtcars[, "disp"]), nrow(mtcars), 3)[,3])

bench::mark(
  model$Y,
  matrix(c(mtcars[, "mpg"]), nrow(mtcars), 1))

bench::mark(
  model$H,
  {X <- matrix(c(rep(1,nrow(mtcars)), mtcars[,"cyl"], data[,"disp"]),nrow(mtcars),3)
  X %*% solve(t(X) %*% X) %*% t(X)})

bench::mark(
  model$Y_hat,
  {X <- matrix(c(rep(1,nrow(mtcars)), mtcars[,"cyl"], data[,"disp"]),nrow(mtcars),3)
  X %*% solve(t(X) %*% X) %*% t(X) %*% mtcars[,"mpg"]}
  )

bench::mark(
  model$residuals,
  {X <- matrix(c(rep(1,nrow(mtcars)), mtcars[,"cyl"], data[,"disp"]),nrow(mtcars),3)
  mtcars[,"mpg"] - c(X %*% solve(t(X) %*% X) %*% t(X) %*% mtcars[,"mpg"])}
  )


```

-   The above code indicates both the **correctness and efficiency** of the function `lm_mat`. `lm_mat` integrates *essential basic information and matrix notation values* of linear regression, which is useful for researchers and statisticians to determine the rationality of the model.


## `coef1`: Parameter estimation and inference of the linear model

```{r}
coef1 <- coef1(model)
## Variable names of the returned list
names(coef1)
```

The description of the variables included is as follows:

-   `Coefficients`: coefficient table same as the one in the lm() table, using calculation as follows:\
    $\hat{\beta}$ is calculated using design matrix $X$ and $Y$: $$\hat{\beta}=(X^{T}X)^{-1}X^TY$$\
    $se(\hat{\beta})$ is calculated using $\hat{\sigma}^2$ and $X$, where:\
    $$\hat{\sigma}^2=\frac{SSE}{dfE}=\frac{\hat{\epsilon}^T\epsilon}{n-p}$$\
    Therefore,\
    $$diag(\hat{var}(\hat{\beta}))=(\hat{var}(\hat{\beta_{0}}), \hat{var}(\hat{\beta_{1}}), ...,\hat{var}(\hat{\beta_{p-1}}))_{1\times p}$$\
    $$t=\frac{\hat{\beta_{k}}}{se(\beta_{k})}$$

-   `F-test`: conduct F-test by using SSR and SSE: $$F = \frac{SSR/(p-1)}{SSE/(n-p)}$$\

-   `Signif.codes`: Significance level denotation

-   `Adj.R_square`: Adjusted R square, calculated by:\
    $$R_{adj}^{2}=1- \frac{SSE/(n-p)}{SSY/(n-1)} $$

-   `R_square`: R square, calculated by:\
    $$R^{2}=1- \frac{SSE}{SSY} $$

-   `Covariance_matrix`: $\hat{var}(\hat{\beta})$, where $(i,j)$ th element $(i≠j)$ is $Cov(\hat{\beta_{i}},\hat{\beta_{j}})$, and the diagonal element is $$\hat{var}(\hat{\beta_{i}})=se(\hat{\beta_{i}})^{2}$$

```{r}
## Using all.equal and bench::mark to check both correctness and efficiency of the function coef1
## Original model
bench::mark(
  summary(lm(mpg~cyl+disp,data=mtcars))$coefficients,
  summary(lm(mpg~cyl+disp,data=mtcars))$coefficients
)

## New model, including significance level
bench::mark(
  coef1$Coefficients,
  coef1$Coefficients
)

## F-test
stopifnot(all.equal(as.numeric(coef1$F_test[1:3]), as.numeric(summary(lm(mpg~cyl+disp,data=mtcars))$fstatistic)))
bench::mark(
  as.numeric(coef1$F_test[1:3]),
  as.numeric(summary(lm(mpg~cyl+disp,data=mtcars))$fstatistic)
)

## Adj. R_square
stopifnot(all.equal(coef1$Adj.R_square,summary(model1)$adj.r.squared))
bench::mark(
  as.numeric(coef1$Adj.R_square),
  as.numeric(summary(model1)$adj.r.squared)
)

## R_square
stopifnot(all.equal(coef1$R_square,summary(model1)$r.squared))
bench::mark(
  as.numeric(coef1$R_square),
  as.numeric(summary(model1)$r.squared)
)

## Covariance matrix
stopifnot(all.equal(coef1$Covariance_matrix, vcov(model1)))
bench::mark(
  as.numeric(coef1$Covariance_matrix),
  as.numeric(vcov(model1))
)

```
-   The above code indicates both the **correctness and efficiency** of the function `coef1`. `coef1` integrates essential linear regression result together into a list, which spares much time for further analysis.


## `model_diag`: Model diagnostics of the established Linear Model

```{r}
model_MLR1 = lm_mat("mpg", c("cyl", "disp", "qsec"), mtcars, beta0 = TRUE)
model_diag(model_MLR1)

## As there is no other function that depicts the same plot as our function, and the variables necessary for those plots (namely residuals, fitted values, etc.) have been verified, we don't use either all.equal() or bench::mark() here.
```

**Figure A.** Normal Q-Q plot, which evaluates how well the distribution of a dataset matches a standard normal (Gaussian) distribution;\
**Figure B.** Scatter plot between Fitted values (Y hat) vs. Residuals), which tests the independence of residuals;\
**Figure C.** Histogram of residuals, which describes the extent of normality of the model;\
**Figure D.** Scatter plot between Fitted values (Y hat) vs. Original Values (Y), which describes the goodness of fit of the model.

## `eda`: Exploratory Data Analysis of the selected variables from linear model

```{r}
eda(model_MLR1$selected)

## As this is a customized function, and there is no function that we can compare with, we don't use either all.equal() or bench::mark() here.
```

-   The above code creates a ($a$ by $a$) matrix (where $a$ is the number of input variables) with one plot at each element. The plot has the following features:

    -   **Lower triangle of the matrix**: Scatter plot and fitted curve between variables\
    -   **Diagonal**: Histograms and names of variables\
    -   **Upper triangle of the matrix**: Correlation coefficients between variables

**Note**: You can set `beta0` = `FALSE` to construct a linear model without intercept.
